---
title: "Assignment 1: Lists, dataframes"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
  html_notebook:
    df_print: paged
    highlight: tango
    self_contained: yes
    theme: paper
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

<div style="font-size:1.5em">
**Make sure your solution to each question includes enough output to show that your solution is correct (i.e if asked to create a vector, output the vector afterwards)**
</div>


##Question #1 - Lists
a. Create the following vectors 
    - `num` = `10` random numbers
    - `sequence` = the sequence of numbers from `1` to `10`, by `.5`
    - `words` = `"this", "is", "super", "fun"`
    - `bool.vals` = `TRUE, FALSE, TRUE, TRUE, FALSE, TRUE, FALSE, FALSE`
    
```{r}
num <- c(1,4,5,7,8,8,6,9,4,5,10)
sequence <- seq(1,10, by=5)
words <- c("this", "is", "super", "fun")
bool.vals <- c(TRUE, FALSE, TRUE, TRUE, FALSE, TRUE, FALSE, FALSE)
```
b. Combine these vectors into a list called `stuff` and make sure each part of the list is named the same as its original vector 
```{r}
stuff <- list(num=num,sequence=sequence,words=words,bool.vals=bool.vals)
```
c. Access the list to output just the words, then just the 3rd word.
```{r}
words[3]
```


##Question #2 - Data Frames


a. Use the `CO2` data from the `datasets` package, and use head to view the top of the file.  
```{r}
library(datasets)
CO2
```
b. Use base R, output the following subsets of the data frame

- Just the `conc` column. 
```{r}
CO2[,c("conc")]
```    
   
- Just the `fifth` row. 
```{r}
CO2[5, ]
```    
- The first `5` rows. 
    
```{r}
CO2[1:5, ]
```    
- Rows `10` to `15`. 
    
```{r}
CO2[10:15, ]
```    
- The `plant`, `Treatment` and `uptake` columns 
    
```{r}
CO2[, c("Plant", "Treatment", "uptake")]
```    
- The rows where `Treatment` equals `chilled`
```{r}
(CO3 <- CO2[with(CO2, Treatment == "chilled"), ]) 
```    

- The rows where `Treatment` equals `chilled` and `uptake` <`10` 
```{r}
(CO3 <- CO2[with(CO2, Treatment == "chilled" & uptake<10), ])
```    

 c. Drop the `Type` column from the data frame
```{r}
within (CO2, rm("Type"))
```

d. Add a column to the dataframe containing the results of `uptake`/`conc` 
```{r}
iris <- within(CO2, ratio <- uptake / conc)
```


